\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Project Specification}
\author{Vass Zóra, D0HAMI}
\date{\today}

\begin{document}
    \maketitle
    \section{Introduction}
    \subsection{Project description}
    My project is going to be an appointment scheduler and manager for service providers. Some examples would be hairdressers, doctors, nail technicians, yoga teachers, etc.
    It keeps these providers' appointments in one place. Customers can reserve appointments anytime online. 
    \subsection{Functionalities}
    \subsubsection*{Reservation for customers}
    %Browse calendar of available appointments of the service provider
    Customers can browse available appointments. It is possible to filter the appointments by date, time, service, and service provider.
    \subsubsection*{Schedule appointments}
    %recurring, restrict number of customers, place. description, price, duration
    Service providers can create appointments. The appointments will have some customizable fields like, number of customers, place, price, duration, etc. 
    \subsubsection*{Calendar view}
    %monthly, weekly, daily
    Users can view their appointments in calendar form. 
    \section{Backend}
    \subsection{Database}
    \subsubsection*{Tables}
    \begin{itemize}
        \item Users: stores the client and service provider users
        \item Appointments: stores the data of appointments given by service providers
        \item Bookings: stores the appointment id and the user's id who booked the appointment
        \item Providers: stores additional information about service provider users
    \end{itemize}
    \subsubsection*{Relations}
    \begin{itemize}
        \item Provider has many Appointments
        \item Booking has one User
        \item Appointments has many Bookings
    \end{itemize}

\end{document}